%! Tex root: ../master.tex

\paragraph{how the BRST structure could be helpful?}

Let's test that whether the BRST structure is restrictive enough such that no new interaction could be generated from the RG calculation.

Let's get a closer look at the action
\[
	-\frac{1}{2}\mathrm{Tr}H^2 + ig \mathrm{Tr}\left([\overline{Z},Z]H\right) + ig \mathrm{Tr}\left([\overline{\Psi},Z]\eta + [\overline{Z},\Psi]\eta\right)
.\] 
Let's assume that $g$ is small and try to do the perturbative calculation.
However, it's not possible because there is no quadratic term.
To solve this, let's deform the action by adding the following term
\[
	i \kappa \delta\left(\mathrm{Tr}(\overline{Z}\Psi - Z \overline{\Psi})\right) = 2i \kappa \mathrm{Tr}\left(\overline{\Psi}\Psi\right) - 2 \kappa \epsilon \mathrm{Tr}\left(\overline{Z}Z\right) - 2i\kappa \mathrm{Tr}\left([\overline{Z},Z]H\right)
.\] 
Because its $\delta$-exact, the deformation is $\delta$-invariant.
$\kappa$ is also a small parameter.
To get the usual quadratic term for $Z$, we choose $\epsilon = 1 / 4\kappa$.
Also note that the action can be simplified if $\kappa = g / 2$ because the term $\mathrm{Tr}\left([\overline{Z},Z]H\right)$ being cancelled.
Let's keep this choice, then the action reads
\[
	- \frac{1}{2} \mathrm{Tr} H^2 - \frac{1}{2} \mathrm{Tr}(\overline{Z}Z) + ig \mathrm{Tr}(\overline{\Psi}\Psi) + ig \mathrm{Tr}\left([\overline{\Psi},Z]\eta + [\overline{Z},\Psi]\eta\right)
.\] 
Or getting back to the matrices $A,B,\psi,\chi$
\[
	- \frac{1}{2}\mathrm{Tr}H^2 - \frac{1}{2}\mathrm{Tr}A^2 - \frac{1}{2}\mathrm{Tr}B^2 - 2 g \mathrm{Tr}(\psi \chi) - 2 g \mathrm{Tr} \left([\psi,B]\eta - [\chi,A]\eta\right)
.\] 

Let's work with $2\times 2$ matrix and use the following parameterization
\begin{align*}
	A = \begin{pmatrix} A & \alpha \\ \alpha^* & a \end{pmatrix},\quad B = \begin{pmatrix} B & \beta \\ \beta^* & b \end{pmatrix} \\
	\psi = \begin{pmatrix} \psi & y \\ y^* & \varphi \end{pmatrix},\quad \chi = \begin{pmatrix} \chi & x \\ x^* & \iota \end{pmatrix} ,\quad \eta = \begin{pmatrix} \eta & h \\ h^* & \theta \end{pmatrix}
\end{align*}
For the $(1,1)$ components, we use the same letter to indicate that they will not be integrated.
Then the quadratic terms have the form
\begin{align*}
	- \frac{1}{2} A^2 - \frac{1}{2} B^2 - \frac{1}{2} a^2 - \frac{1}{2} b^2 - \alpha^* \alpha - \beta^* \beta \\
	- 2g \psi\chi - 2g y x^* - 2g x y^* - 2g \varphi \iota
\end{align*}
The interaction term $ -2 g \mathrm{Tr}([\psi,B]\eta - [\chi,A]\eta)$ contains
\begin{align*}
	-2 g \psi \beta h^* + 2 g \beta^* \psi h - 2g y^* B h + 2 g B y h^* - 2 g y \beta^* \eta + 2 g \beta y^* \eta \\
	+2 g \chi \alpha h^* - 2 g \alpha^* \chi h + 2g x^* A h - 2 g A x h^* + 2 g x \alpha^* \eta - 2 g \alpha x^* \eta \\
	-2 g y^* b h + 2 g b y h^* - 2g \varphi \beta h^* + 2g \beta^* \varphi h - 2g y^* \beta \theta + 2g \beta^* y \theta \\
	+2 g x^* a h - 2 g a x h^* + 2g \iota \alpha h^* - 2g \alpha^* \iota h + 2g x^* \alpha \theta - 2g \alpha^* x \theta 
\end{align*}
There is an additional term that only involving the $(1,1)$-component.
It has the same form with the initial action $ -2 g \mathrm{Tr}([\psi,B]\eta - [\chi,A]\eta)$.

For the Grassmann integral, to get non-vanishing result, one needs to saturate the measure $\mathrm{d}y \mathrm{d}y^* \mathrm{d}\varphi \mathrm{d}x \mathrm{d}x^* \mathrm{d}\iota \mathrm{d}h \mathrm{d}h^* \mathrm{d}\theta$.
Because there is no quadratic term of $\eta$, the non-vanishing terms must include $hh^*\theta$.
For other variables, if they appear, they must form the pairs
\[
a^2,\quad b^2,\quad \alpha^* \alpha,\quad \beta^* \beta,\quad y x^*,\quad x y^*,\quad \varphi \iota
.\]
For fermionic variables $yx^*,xy^*,\varphi\iota$, they must not appear more than one time.
These are the basic constraints to get non-vanishing integral result.

First note that $h,h^*,\theta$ appear in each term once.
Therefore, to get non zero result, one needs at least the cubic term
\[
	- \frac{4}{3} g^3 \left[\mathrm{Tr}([\psi,B]\eta - [\chi,A]\eta)\right]^3
.\] 
Let's focus on the terms that containing these combinations: $\psi B, \psi A, \chi B, \chi A$. One would expect that all of them being vanish because they have an odd number of fermionic variables. For $\psi B, \chi A$, to fully contract the variables, one needs terms containing $x\beta^*,y\alpha^*$. There is no such term. For $\psi A$, one selects the following terms
\[
	(-\psi \beta h^*)(x^* A h)(\beta^* y \theta) + (\beta^* \psi h) (- A x h^*) (- y^* \beta \theta)
.\] 
By contracting $hh^*,xy^*,yx^*$ one finds that the result being zero.
Similar for $\chi B$. So it's in accordance with the expectation.
(TODO: analyze other terms like $A^2,AB,B^2,\psi\chi$)

It's easy to understand that $\left[\mathrm{Tr}([\psi,B]\eta - [\chi,A]\eta)\right]^5$ always vanishing because one of the $h,h^*,\theta,\eta$ will appear twice. So one only need to consider the quartic term
\[
\frac{2}{3} g^4 \left[\mathrm{Tr}([\psi,B]\eta - [\chi,A]\eta)\right]^4
.\] 
Out of all possible combinations, it may be interestring to consider those containing $\psi\eta$ and $\chi\eta$ first.
To find the terms that containing $\psi\eta$, one first select $(-\psi\beta h^*)$ or $(\beta^* \psi h)$.
Let's take the first choice as an example.
Then one needs to add a term that containing $h$ but not containing $A,B,\chi$ because we only focus on $\psi\eta$.
The possibilities are the following
\[
	- y^* b h,\quad x^* a h,\quad \beta^* \varphi h,\quad -\alpha^* \iota h
.\] 
Each of them containing one of $a,b,\varphi,\iota$.
To get non-vanishing result, one needs another term that only containing one of them.
But there is no such term: they either contain $\varphi b,\iota a$ or containing none of them.
Therefore, $\psi\eta$ will not be generated through the perturbative calculation.

It's also easy to see that the terms like $A\psi\chi$ will not be generated because $h,h^*$ would be over-saturate.
Then it's interesting to consider $\psi A \eta$ which does not appear in the original action.
For example, one starts by selecting the two terms
\[
	(-\psi \beta h^*) (x^* A h)
.\] 
Then one must select the term $(- y \beta^* \eta)$ that containing $\eta$.
Because otherwise $\beta,x^*$ cannot be contracted.
However, then one must include also an extra $\theta$ term to saturate $\mathrm{d}\theta$.
Any of them will contain one of $\alpha,\beta,\varphi,\iota,a,b$ that having no partner to contract.
Therefore, no $\psi A \eta$ could be generated.

let's consider another possible new term $\psi\chi\eta$.
It contains three fermionic variables, therefore being expected to vanish.
Let's verify it explicitly.
The following terms would contribute to $\psi\chi\eta$
\[
	(-\psi \beta h^*) (- \alpha^* \chi h) \left[(-y \beta^* \eta)(x^* \alpha \theta) + (-\alpha x^* \eta)(\beta^* y \theta)\right]
.\] 
\[
	(\beta^* \psi h)(\chi \alpha h^*)\left[(\beta y^* \eta)(\alpha^* x \theta) + (x \alpha^* \eta)(-y^* \beta \theta)\right]
.\] 
It's straightforward to check they vanish because the order of $y,x^*$ and $y^*,x$ are different in the two terms.

It turns out that nothing could be generated from integrating out those variables.
Then the question is that whether the same thing hold for general $N$?
