%! Tex root: ../master.tex
\newpage

\begin{problem}[IKKT]
	Apply the RG method to IKKT,
	try to find out the scaling behavior of the $g_{YM}$.
	There are various motivations that lead to consider the $N\to\infty$ limit.
	A natural question is then whether this limit is well-defined?
	What's the meaning of ``well-defined''?
\end{problem}

The bosonic part of IKKT based on the matrix function
\[
	\mathrm{Tr}[A^\mu,A^\nu][A_\mu,A_\nu],\quad \mu,\nu=0,\cdots,9
.\] 
$A^\mu$ are $N\times N$ Hermitian matrices.
It's natural to take $A^\mu$ as elements in the Lie algebra
$\mathfrak{su}(N)$,
because the IKKT model is obtained by reducing the Yang-Mills theory.
One could be more careful:
the gauge algebra could be $\mathfrak{u}(N)$;
also one could equivalent two matrices that are equal up to a permutation of rows and columns.

The difference between
$\mathfrak{su}(N)$ and $\mathfrak{u}(N)$ is
whether the matrices are traceless.
Looking at the matrix function, one notices that
$A\to A + \lambda\mathds{1}$
is a symmetry of it.
This means that one could impose the traceless condition
by ``gauge fixing''
(properly factor out the integral over the trace).
However, it's not always possible to construct a $(N-1)\times(N-1)$ traceless matrix from a $N\times N$ traceless matrix by killing one row and one column.

\begin{question}
	What's the proper way to deal with the trace?
\end{question}

Consider $A_0^\mu$ be $(N+1)\times(N+1)$ Hermitian matrices.
$A^\mu$ be $N\times N$ Hermitian matrices embedded as
\[
	A_0^\mu = \begin{pmatrix} A^\mu & \alpha^\mu \\ (\alpha^\mu)^\dagger & a^\mu \end{pmatrix}
.\] 
Note that the symmetry $A_0 \to A_0 + \lambda \mathds{1}$ will
not be realized as a similar translation symmetry of $A$
because one should translate $a$ at the same time.

The action $\mathrm{Tr}[A_0,A_0]^2$ decomposes as the following:
\begin{align*}
	\mathrm{Tr}[A_0^\mu,A_0^\nu][A_{0\mu},A_{0\nu}] = 
	\mathrm{Tr}[A^\mu,A^\nu][A_{\mu},A_{\nu}] 
	\\
	+ 2(\alpha^\mu)^\dagger (2 A_\nu A_\mu - A_\mu A_\nu -  A^2 \eta_{\mu\nu}) \alpha^\nu
	\\
	- 2 (\alpha^\mu)^\dagger (a_\mu A_\nu + a_\nu A_\mu - 2 a^\rho A_\rho \eta_{\mu\nu}) \alpha^\nu
	\\
	+ 2 (\alpha^\mu)^\dagger (a_\mu a_\nu - a^\rho a_\rho \eta_{\mu\nu}) \alpha^\nu
\end{align*}
the terms that are quartic in $\alpha^\mu$
\[
2 \left[	(\alpha^\mu)^\dagger \alpha^\nu (\alpha_\mu)^\dagger \alpha_\nu 
- (\alpha^\mu)^\dagger \alpha^\nu (\alpha_\nu)^\dagger \alpha_\mu
- (\alpha^\mu)^\dagger \alpha_\mu (\alpha^\nu)^\dagger \alpha_\nu \right].
\] 
Is it possible to ``complete the square''?
For example consider
\[
\mathrm{Tr} \left( \alpha^\mu (\alpha^\nu)^\dagger
 + a \alpha^\nu (\alpha^\mu)^\dagger
+ b \eta^{\mu\nu} \alpha^\rho (\alpha_\rho)^\dagger\right)^2
.\]
It's equal to
\[
	(1+a^2) (\alpha^\mu)^\dagger \alpha^\nu (\alpha_\mu)^\dagger \alpha_\nu
	+ (D b^2 + 2 b + 2 a b) (\alpha^\mu)^\dagger \alpha^\nu (\alpha_\nu)^\dagger \alpha_\mu
	+ 2a (\alpha^\mu)^\dagger \alpha_\mu (\alpha^\nu)^\dagger \alpha_\nu
.\] 
By choosing $a,b$ we could recover the quartic term (up to an overall constant).

\begin{problem}[scaling with N]
	On one hand, we want to take the 't Hooft limit
	\[
		g_0^2 N_0 = \text{fix},\quad N_0\to\infty
	.\] 
	We use the subscript ``0'' to indicate these quantities are defined at the ``cut-off'' in the RG sense.
	Consider along the RG flow, we get a theory with matrix size $N$,
	with the following action
	\[
		\frac{1}{g^2} \mathrm{Tr} [A,A]^2
	.\] 
	The question is how $g$ flows with $N$.
	(not how $g_0$ changes with $N_0$ in the 't Hooft limit)
\end{problem}

\begin{todo}
	Learn about the ``Gaussian expansion method''.
	Think about the large D expansion.
\end{todo}
